Final Presentation

### 2017-01-26 final_presentation.Rmd
edit date
github link

---
title: "Final Presentation"
author: "Dylan Sun & Zijiang Yang"
date: '2017-01-17'
output:
  slidy_presentation: 
    font_adjustment: +2
---

>>>>

---
title: "Final Presentation"
author: "Dylan Sun & Zijiang Yang"
date: '2017-01-26'
output:
  beamer_presentation: default
  slidy_presentation:
    font_adjustment: 2
---
